---
title: "Music - Lessons - Flamenco"
output:
  html_document:
    toc: true  
    toc_float: true 
---

# Theory

From "Music Theory For Flamenco" by "Flamenco Chuck" Keyser 1998.

<br><br>

Natural scale (without any sharps or flats): C D E F G A B C

## Flamenco Modes & Scales



# Techniques

```{r results="asis", echo=FALSE}
Technique <- c("Picado","Tremolo","Alzapua","Arpeggio","Pulgar","Rasgueado - 3 finger","Rasgueado - 4 finger")
BMP <-       c(80      ,       80,       80,        80,      80,                    80,                    80)
Beats <-     c(4       ,        4,        4,         4,       4,                     4,                     4)
Minutes <-   c(1       ,        1,        1,         1,       1,                     1,                     1)
Date <- c("14Dec2017"  ,      "x",      "x",      "x",      "x",                   "x",                   "x")
tab<-data.frame(Technique,BMP,Beats,Minutes,Date)
library(knitr)
kable(tab,align='lccc')
```


```{r bunch_o_figs_svg, fig.height=4, fig.width=8, dev='svg',echo=FALSE}
x<-data.frame(
  Date=c("16Dec2007","17Dec2007","18Dec2007"),
  Rasgueado_3Finger=c(1,2,3),
  Rasgueado_4Finger=c(3,NA,5))
x$Date<-as.Date(x$Date,format="%d%b%Y")
par(mfrow=c(1,2), las=1)
for(i in 2:ncol(x)) {
  plot(x[[1]], x[[i]], main=names(x)[[i]],xaxt="n",type="o")
  axis.Date(1, at=seq(min(x$Date), max(x$Date), by="1 week"), format="%d%b%Y")
  text(min(x$Date), 0.8*max(x[[i]]), paste("Best BMP =",sep=""),cex = .8)
}
```

* Rasgueado


# Toques

# Lessons

## Graf Martinez - Flamenco Guitar Method

```{r results="asis", echo=FALSE}
Lesson <- c("T1 - Sencillos 1 (Tangos)","T2 - Estudio por Solea")
Technique <- c("1 Finger Rasgueado","3 Finger Rasgueado")
BMP <- c(120,0)
Minutes <- c(1,0)
Date <- c("14Dec2017","x")
tab<-data.frame(Lesson,Technique,BMP,Minutes,Date)
library(knitr)
kable(tab,align='llccc')
```

## Atrafana School - 

## Juan Martin - El arte de flamenco
## Aaron Gilmartin - Learn to play flamenco guitar
## Manuel Granados - Manual Guitarra Flamenca
## Paco Pena - Toques Flamenco

# Reportoire

# Listening
